Collective behavior of Janus Particles Suspended in a Viscous Fluid

### 2022-07-20 doc/PRF2022/PRF_main.tex
yny 0720 5

$\FF_i$ and $T_i$ are to be in balance with the force and torque from the hydrophobic interactions between the
particles and the viscous solvent. As in \citet{Fu2022_JFM} such a hydrophobic attraction potential $u(\xx,t)$ is assumed to
the minimizer of the free energy
\begin{equation}
\label{eq:free_energy}
F = \gamma
\int_{\Omega} \rho |\nabla u|^2 + \rho^{-1} u^2
\,d\xx
+ \frac{M}{2}
\sum_{j \neq i} 
P\left(\frac{|\aa_i - \aa_j|-2c}{\rho_0}\right), \quad
\end{equation}
where the hydrophobic attraction potential $u(\xx,t)$ can be regarded as an order parameter for the structure of water,
$\rho$ is a decay length, and $\gamma$ is an interfacial tension. 
$c$ is an ``effective" inter-particle distance below which the steric repulsion between a pair of JPs becomes important.

@@

\section{Equilibrium configurations}
\subsection{Boundary conditions and normalization}
The present paper considers boundary conditions of the form
\begin{equation}
  \label{eq:bc-type}
g(\xx) = a(b + \cos \alpha),\quad a = (\pi c(2b^2 + 1))^{-1/2},\quad \xx \in \Gamma_i,
\end{equation}
where $\alpha$ is the angle between $\xx - \aa_i$ and the particle director
$\dd_i = (\cos \theta_i, \sin \theta_i)$.
The parameter $a$ normalizes the boundary conditions 
so that $\int_{\Gamma_i} g^2(\xx) \, \dif s = 1$.
The motivation for this normalization is that the hydrophobic attraction
part of the free energy converges to the integral of the square of the boundary
data in the zero-screening length limit.  
We refer to the side of the particle where $\alpha = 0$
as the tail and the side where $\alpha = \pi$ as the head.

To see the effect of the shift parameter $b$, we simulate the dynamics of
198 particles and 60 particles in a quiescent flow as shown in Figure~\ref{fig:relax}.
Three distinct configurations emerge:
(i) bilayers for $b = 1$, 
(ii) multilamellar for $b = 2$, and 
(iii) striated for $b = 0$.

>>>>

$\FF_i$ and $T_i$ are to be in balance with the force and torque from the hydrophobic interactions between the
particles and the viscous solvent. As in \citet{Fu2022_JFM} such a hydrophobic attraction potential $u(\xx,t)$ is assumed to
the minimizer of the free energy
\begin{equation}
\label{eq:free_energy}
F = \gamma
\int_{\Omega} \rho |\nabla u|^2 + \rho^{-1} u^2
\,d\xx
+ \frac{M}{2}
\sum_{j \neq i} 
P\left(\frac{|\aa_i - \aa_j|-2c}{\rho_0}\right), \quad
\end{equation}
where the hydrophobic attraction potential $u(\xx,t)$ can be regarded as an order parameter for the structure of water,
$\rho$ is a decay length, and $\gamma$ is an interfacial tension. 
$c$ is an ``effective" distance between particle centers, below which the steric repulsion between a pair of JPs becomes important.
In the followings we use the radius of JP for $c$.

@@

\section{Equilibrium configurations}
\subsection{Boundary conditions and normalization}
The present paper considers boundary conditions of the form
\begin{equation}
  \label{eq:bc-type}
g(\xx) = a(b + \cos \alpha),\quad a = (\pi c(2b^2 + 1))^{-1/2},\quad \xx \in \Gamma_i,
\end{equation}
where $\alpha$ is the angle between $\xx$ and  $\aa_i$, and 
$\dd_i = (\cos \theta_i, \sin \theta_i)$ isthe particle director.
The parameter $a$ normalizes the boundary conditions 
so that $\int_{\Gamma_i} g^2(\xx) \, \dif s = 1$.
The motivation for this normalization is that the hydrophobic attraction
part of the free energy converges to the integral of the square of the boundary
data in the zero-screening length limit.  
We refer to the side of the particle where $\alpha = 0$
as the tail and the side where $\alpha = \pi$ as the head.

The boundary condition on JP can be put into three categories: min$(g) >0$, min$(g) =0$, and min$(g) <0$. Without loss of generality, 
these three categories correspond to three characteristic values of $b$ in \eqref{eq:bc-type}: $b=2$, $b=1$ and $b=0$, respectively. 
%
To see the effect of the shift parameter $b$, we simulate the dynamics of
198 particles and 60 particles in a quiescent flow as shown in Figure~\ref{fig:relax}.
Three distinct configurations emerge:
(i) bilayers for $b = 1$, 
(ii) multilamellar for $b = 2$, and 
(iii) striated for $b = 0$.
